 ---
title: "Movielens"
date: '`r Sys.time()`'
output:
  html_document:
    #code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
library(scales)
library(tidyverse)
library(knitr)

# set plot theme
theme_set(theme_bw())
```

# Load and preview data

# for reference: same thing, using base R functions and explicitly setting column information
   ratings <- read.delim('ratings.csv',
                         sep=',',
                         header=F,
                         col.names=c('user_id','movie_id','rating','timestamp'),
                         colClasses=c('integer','integer','numeric','integer'))

#Read data from the `ratings.csv` file

```{r load-data}
 
# Summary statistics

``` {r dist-ratings}
# plot the distribution of rating values (slide 21)
ratings %>% 
  group_by(rating) %>% 
  summarise(num_rating = n()) %>% 
  ggplot( aes(x= rating, y= num_rating)) +
          geom_bar(stat = "identity") +
  ylab('Numer of ratings')
         
```

## Per-movie stats

```{r aggregate-by-movie}
# aggregate ratings by movie, computing mean and number of ratings
# hint: use the n() function for easy counting within a group
ratings %>% group_by(movie_id) %>% summarise(mean_rating = mean(rating), count = n())

```

```{r dist-movie-popularity}
# plot distribution of movie popularity (= number of ratings the movie received)
# hint: try scale_x_log10() for a logarithmic x axis
ratings %>% 
  group_by(movie_id) %>% 
  summarise(num_rating = n()) %>%
  ggplot(aes(x=num_rating)) +
  geom_histogram() +
  scale_x_log10(label=comma) +
  scale_y_continuous(label= comma)+
  xlab('Movie rating')+
  ylab('Number of rating')

```

```{r dist-mean-ratings-by-movie}
# plot distribution of mean ratings by movie (slide 23)
# hint: try geom_histogram and geom_density
ratings %>% 
  group_by(movie_id) %>% 
  summarise(mean_rating = mean(rating)) %>% 
  ggplot(aes(x=mean_rating)) +
  geom_density(fill="black") +
  xlab('Mean rating by movie')

```

```{r cdf-movie-pop}
# rank movies by popularity and compute the cdf, or fraction of movies covered by the top-k moves (slide 25)
# hint: use dplyr's rank and arrange functions, and the base R sum and cumsum functions
# store the result in a new data frame so you can use it in creating figure 2 from the paper below
rating_count= nrow(ratings)
ratings %>% group_by(movie_id) %>% 
  summarise(num_rating = n()) %>% 
  mutate(movie_rank= rank(desc(num_rating), ties.method = c("first"))) %>%
  arrange(movie_rank) %>% mutate(cs = cumsum(num_rating)/rating_count) %>%
  ggplot(aes(movie_rank, cs)) +
  geom_line()+
  ylab('CDF') +
  xlab('Movie Rank') +
  scale_y_continuous(label=comma)

# plot the CDF of movie popularity

```


# Per-user stats

```{r aggregate-by-user}
# aggregate ratings by user, computing mean and number of ratings
ratings %>% group_by(user_id) %>%
  summarize(num_rating= n(), mean_rating= mean(rating))
```

```{r dist-user-activity}
# plot distribution of user activity (= number of ratings the user made)
# hint: try a log scale here

ratings %>% group_by(user_id) %>%
  summarize(num_rating= n()) %>%
  filter(num_rating < quantile(num_rating, .99)) %>%
  ggplot(aes(x=num_rating)) +
  geom_histogram()+
  scale_x_log10(label=comma) +
  scale_y_continuous(label= comma)+
  xlab('User Activity')+
  ylab('Number of rating')

```

# Anatomy of the long tail

```{r long-tail}
# generate the equivalent of figure 2 of this paper:
# https://5harad.com/papers/long_tail.pdf

# Specifically, for the subset of users who rated at least 10 movies,
# produce a plot that shows the fraction of users satisfied (vertical
# axis) as a function of inventory size (horizontal axis). We will
# define "satisfied" as follows: an individual user is satisfied p% of
# the time at inventory of size k if at least p% of the movies they
# rated are contained in the top k most popular movies. As in the
# paper, produce one curve for the 100% user satisfaction level and
# another for 90%---do not, however, bother implementing the null
# model (shown in the dashed lines).

population <- ratings %>% 
  group_by(movie_id) %>% 
  summarise(numrating = n())%>% 
  mutate (rank = rank(desc(numrating), ties.method = "last"))

cutoff_100_count <- ratings %>% group_by(user_id) %>%
  summarise(cutoff= n()) 

cutoff_90_count <- ratings %>% group_by(user_id) %>%
  summarise (cutoff = ceiling(.9*n()))

selfrank <- ratings %>% left_join(population) %>%
  group_by(user_id) %>%
  mutate(self_rank = rank(rank, ties.method = "last"))

cutoff_90 <- left_join(selfrank, cutoff_90_count) %>% 
  filter(cutoff == self_rank) %>%
  select(user_id, rank)

cutoff_100 <- left_join(selfrank, cutoff_100_count) %>% 
  filter( cutoff == self_rank) %>%
  select(user_id, rank)

user_count <- nrow(cutoff_100)
 
final_100 <- cutoff_100 %>% 
  group_by(rank) %>% 
   summarise(num_user = n()/user_count) %>% 
   arrange(rank) %>%
   mutate(cs = cumsum(num_user), set_level="100%")

 final_90 <- cutoff_90 %>% 
   group_by(rank) %>% 
   summarise(num_user = n()/user_count) %>% 
   arrange(rank) %>%
   mutate(cs = cumsum(num_user), set_level="90%")
 
 bind_rows(final_100,final_90) %>% 
   ggplot(aes(x=rank, y= cs, color = set_level)) +
   geom_line() +
   xlab ('Inventory Size') +
   ylab('Percent of User Satisfied')
 

```
