#---
title: "OrangeJuice"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

oj <- read.csv('oj.csv')
str(oj)
```

``` {r}
library(ggplot2)
#a.	Make a box plot of price.

ggplot(oj, aes(x= "", y=price)) + 
  geom_boxplot()

```

```{r}
#b.	Make a box plot of log price.
library(tidyverse)
oj %>% mutate(logprice = log(price)) %>% 
  ggplot(aes(x="", logprice)) + 
  geom_boxplot()
  
```

```{r}
#c.	Make a box plot of price, but separate out each brand.

ggplot(oj, aes(factor(brand), price)) + 
  geom_boxplot(aes(fill = factor(brand)))

```

``` {r}
#d.	Do the same for log price. 
oj %>% mutate(logprice = log(price)) %>% 
  ggplot(aes(factor(brand), logprice)) + 
  geom_boxplot(aes(fill = factor(brand)))

#e.	What do these graphs tell you about the variation in price? Why do the log plots look different? Do you find them more/less informative?

```
The log price is more informative because: the variance between log group looks identical and the outliers are more spread out. Hence, we can tell the variance within group better. 
```{r}
#	Plot logmove (log quantity) vs. log(price) for each brand.  For this one the appropriate second part of the ggplot command will be: + geom_point(aes(color = factor(var_name)))
oj %>% mutate(logprice = log(price)) %>% 
  ggplot(aes(logmove, logprice)) + 
  geom_point(aes(color = factor(brand)))

#i.	What do insights can you derive that were not apparent before?

```
The lower the price, the more quantity sold. However, at the same level of price, the more well-known the brand, the more quantity sold.

```{r}
# a.	Do a regression of log quantity on log price. How well does the model fit? What is the elasticity, does it make sense?

reg_mod <- oj %>% mutate(logprice = log(price)) %>% lm(formula= logmove ~ logprice)
summary (reg_mod)

oj <- oj %>% mutate(logprice = log(price))

```
```{r}
#add in an intercept term for each brand (add brand to the regression)
intercept_reg_mod <- lm(formula= logmove ~ logprice + brand, data = oj)
summary(intercept_reg_mod)

```

```{r}
#figure out a way to allow the elasticities to differ by brand
interaction_reg_mod <- lm(formula= logmove ~ logprice + brand + logprice*brand, data = oj)
summary(interaction_reg_mod)
```

```{r}
## 80% of the sample size
smp_size <- floor(0.8 * nrow(oj))

## set the seed to make your partition reproducible
set.seed(1)
train_ind <- sample(seq_len(nrow(oj)), size = smp_size)

train <- data.frame(oj[train_ind, ])
test <- data.frame(oj[-train_ind, ])

interaction_reg_train <- lm(formula= logmove ~ log(price) + brand + log(price)*brand, data = train)
summary(interaction_reg_train)

y_hat <- predict(interaction_reg_train, newx = test)

```

According to the plot, Minute Maid is featured the most accross brand over the time.
```{r}
oj %>% group_by(store, brand,feat) %>%
  summarise(count= n()) %>% filter(feat == 1) %>%
  ggplot(aes(store, count, color= as.factor(brand), position= "jitter")) +
  geom_point()

ggplot(oj, aes(feat, brand)) + geom_point(position = "jitter", aes(color= factor(brand)))
```

```{r} 
#	What is the average price and featured rate of each brand?  
 oj %>% group_by(brand) %>% summarise(avg_price= mean(price), avg_feat= mean(feat))

library(plyr)
ddply(oj, .(brand,feat), summarise, mean_price= mean(price), sd_price=sd(price), obs= length(price))

?glm
```
```{r}
#incorporate the feature variable into our regression
intercept_reg_mod2 <- lm(formula= logmove ~ log(price) * brand + feat, data = oj)
summary(intercept_reg_mod2)

interaction_reg_mod2 <- lm(formula= logmove ~ log(price) * brand + feat + feat*logprice, data = oj)
summary(interaction_reg_mod2)

socio_mod <- lm(formula= logmove ~ log(price) * brand + feat + feat*logprice + AGE60, data = oj)
summary(socio_mod)

```


