---
title: "Q12.1 - Hypothesis Testing"
author: "Phoebe"
date: "June 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let X be the measurement of change, the difference between the score of
pain before the treatment and the score after the treatment, for patients
that were treated with the inactive placebo. Express, in terms of the
expected value of X, the null hypothesis and the alternative hypothesis
for a statistical test to determine the presence of a placebo effect. 
H0: E(X) = 0
H1: E(X) <> 0

To test the hypothese, we use the last 21 observations in the file "magnets.csv", which were the patient whom treated
with devises that looked like magnets but actually were not.

```{r read data}
df <- read.csv("magnets.csv")
placebo <- tail(df, 20)

t.test(placebo$change)
```
According to the big t-test (>1.96) and significant p-value, we can reject null hypothesis and accept the alternative hypothesis, which is there is a change in pain level between pre and post treatment with placebo.

## Chap 13 Comparing 2 samples

1. Is there a significant difference between the treatment and the control groups in the expectation of the reported score of pain before the application of the device? 

H0 : E(Xa) = E(Xb)
Ha : E(Xa) <> E(Xb)

```{r}

t.test(df$score1 ~ df$active)

```

2. Is there a significance difference between the treatment and the control groups in the variance of the reported score of pain before the application of the device?
```{r}

var.test(df$score1 ~ df$active)

```
3. Is there a significance difference between the treatment and the control groups in the expectation of the change in score that resulted from the application of the device?
It is significant so we reject null hypothesis and conclude that there is a difference.

```{r}
t.test(df$score2 ~ df$active )

```
4. Is there a significance difference between the treatment and the control
groups in the variance of the change in score that resulted from the application
of the device?
It is changing the variation around the mean.
```{r}
var.test(df$score2 ~ df$active)
```
Make a plot of the distribution of outcomes (score1) split by the treatment (active), similar to this plot
```{r}
library(dplyr)
library(tidyverse)
df %>% ggplot(aes(fill= active)) + geom_histogram(aes(change), position = "dodge", alpha= 0.6)
```

Estimate the effect size by calculating Cohen's d. Think about whether the effect seems practically meaningful.
```{r}

stdv <- sd(df$change)
df %>% group_by(active) %>% summarise(avg = mean(change), count = n()) %>%
  summarise(cohen_d= (first(avg)-last(avg))/stdv)


```
