---
title: "Naive Bayes R Lab"
author: "Phoebe"
date: "June 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Suppose you have a database on four customers. You know their income and whether or not they bought your product. Create a data frame

```{r dataframe}
db <- data.frame(income=c("high","high","medium","low"), 
                    buy=c("yes","no","no","yes"))

```

Using Bayes rule calculate the probability that a customer will buy your product given that he or she has high income.

```{r bayes}
library(e1071)
classifier <- naiveBayes(buy ~ income,db)
classifier

```

What is the prior probability of someone buying your product? What is the probability that a customer has a high income give that he or she bought your product?

```{r}

predict(classifier, data.frame(income= factor('high'), type = "raw"))

```
Using the model you estimated above predict the probability of buying given that a customer has high income. Is your result the same as the one you calculated by hand in question 1?

Suppose you have a database on four customers. You know their gender, income and whether or not they bought your product. Create a data frame with this data.

```{r dataframe}
db2 <- data.frame(income=c("high","high","medium","low"), 
                    buy=c("yes","no","no","yes"),
                 gender=c("male","female","female", "male"))
```
Using Bayes rule calculate the probability that a customer will buy your product given that he has high income and male.
```{r}

classifier2 <- naiveBayes(buy ~ income + gender,db2)
classifier2

```

```