---
title: "Regression Discontinuity"
author: "Phoebe"
date: "June 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Regression Discontinuity on Incumbency E???ect (Lee, 2007)



```{r read data} 
lee <- read.csv('Lee(2007)_RDReplication.csv')
library(dplyr)
library(tidyverse)
```

DemWin (whether or not dems win the current election) lets us know if democrats have the incumbency and it is our treatment of interest. Run a simple regression to try and predict DWinNxt with DemWin. Observe the coe???cient on DemWin. Do you think it gives an unbiased estimate of the incumbency e???ect. Why or why not? 
The coefficient is positive and significant. It means that if Democrate won last term, they are predicted to have 91% chance to win next term.

```{r}
reg1 <- lm(DWinNxt ~ DemWin, data= lee)
summary(reg1)  

```
Introduce some/all of these variables to your regression and see what happens to the coe???cient on DemWin. Di???DPct tells us how much Dems won/lost by in the previous election, this is our running variable that gives us a discontinuity. ForgnPct, GovWkPct, BlackPct, UrbanPct, DWinPrv, YearElec, and CDNum are potential control variables about each congressional district that can help us predict winners. 
 
 Confounding: BlackPct, UrbanPct, ForgnPct, DWinPrv
 
 Unrelated: CDNum, GovWkPct, YearElec
 

```{r}
df <- lee %>% select('ForgnPct', 'GovWkPct', 'BlackPct', 'UrbanPct', 'DWinPrv', 'YearElec', 'CDNumAtL', 'DemWin', 'DifDPct','DWinNxt')

reg2 <- lm(DWinNxt ~ ForgnPct + BlackPct + DWinPrv + DemWin, data= df)
summary(reg2) 

df$y_hat <- predict(reg2,df)

summary(df$y_hat)


cor(na.omit(df$ForgnPct), na.omit(df$BlackPct))

```

(d) Give an additional example of a bad control variable in this setting. It does not have to be one that it is present in the dataset. 
```{r}
reg3 <- lm(DWinNxt ~ SoSDem , data= lee)
summary(reg3)

```
(e) Now use DifDPct as a forcing variable to run a regression discontinuity to estimate the incumbency advantage. Generate a cubic polynomial and pick a window of 10% (this just means to drop data that is more than 15% from the discontinuity) on either side of the threshold (50%). Run a regression discontinuity. How does the coe???cient you got compare to in (b) and (c).
DemWin is smaller than previous model. Hence, the incumbency is real but slightly less significant than the previous one.

```{r}

rd <- lee %>% filter(DifDPct > -10 & DifDPct < 10) 

reg4 <- lm(DWinNxt ~ DemWin * poly (DifDPct, 3, raw= TRUE), data= rd)
summary(reg4)

rd$y_hat <- predict(reg4,rd)
  
rd %>% ggplot(aes(DifDPct, y_hat)) +
  geom_point()+
  geom_smooth(aes(color = factor(DemWin)))
```
(f) Finally, install and use the package rdd to implement this same regression discontinuity design (this saves you from having to decide on bandwidths and code polynomials). 
Use the functions RDestimate and plot to do a faster regression discontinuity anlaysis. 
Your answer in (e) should look somewhat similar to your answer here.

The bandwidth is the window size. We want to have several bandwidths to pick and choose more variables. This will give us the control over the bias-variance trade-off.

```{r}
library('rdd')
rds <- RDestimate(DWinNxt ~ DifDPct, rd)
summary(rds)
plot(rds)
```
